\ex.\label{sent:ex1}Absolutive and Gentitive Forms of 1\Sg[] pronoun: c.f. Figure \ref{fig:ex1} for tree \\ 
    \ag.Zun ata-na. \\
        I:\Abs[] come-\Aori[] \\
        ``I came. (251)
    \bg. [Zi [\v{g}we\v{c}'i wax]] ata-na. \\
        [I:\Gen[] [little sister]] came-\Aori[] \\
        ``My little sister came. (251)
    \z.

\ex.\label{sent:ex7}Selected Verb Forms of \textit{fin} ``go" (127). Verb forms do not exhibit agreement. Trees for a, b, c represented in Figure \ref{fig:sent7} \\
    \ag.fi-zwa \\
    go-\Impf[] \\
    \bg.fi-zwa-\v{c} \\
    go-\Impf[]-\Neg[] \\
    \cg.fi-zwa-j \\
    go-\Impf[]-\Pst[] \\
    \dg.fe-nwa \\
    go-\Prf[] \\
    \z.

\ex. \label{sent:ex4}Question Types: Polar, Binary-Choice, Constituent, Embdedded Polar, Embedded Constituent, Embedded Alternative:  \\
    \ag.\label{sent:ex4a}Betxoven.a-n muzyka wa-z k'an-da-ni? \\
    Beethoven.\Obl[]-\Gen[] music you-\Dat[] like-\Fut[]-\Q[] \\
    ``Do you like Beethoven's music?" (417) (c.f. Figure \ref{fig:sent4a})
    \bg.\label{sent:ex4b}Professor.di ktab k'el-zawa-j-di j-ani ja ta\^{x}ajt'a k\^{x}i-zwa-j-di ja-ni? \\
    professor(\Erg[]) book read-\Impf[]-\Ptcp[]-\Sbstz[] \Cop[]-\Q[] or or write-\Impf[]-\Ptcp[]-\Sbstz[] \Cop[]-\Q[] \\
    ``Is the professor reading or writing a book?" (418) (c.f. Figure \ref{fig:sent4b})
    \bg.\label{sent:ex4c}Farid ata-na-ni? \\ 
    Farid come-\Aori-\Q \\
    ``Has Farid come?" (7)
    \bg.\label{sent:ex4d}Farid mus ata-na \\
    Farid when come-\Aori \\
    ``When did Farid come?'' (8)
    \bg.\label{sent:ex4e}Wun hi\^{x}tin dust.uni-n muq'uw mus fe-na? \\
    you:\Abs[] which friend-\Gen[] to when go-\Aori[] \\
    ``When did you go to which friend?'' (425)
    \bg.\label{sent:ex4f}Za sadra, kkal.i xa-nwa-t'a, akwa-n. \\
    I:\Erg[] \Pt[] [cow(\Erg[]) bear-\Prf[]-\Cond[]] see-\Hort[] \\
    ``Let me see whether the cow has calved.'' (425)
    \bg.\label{sent:ex4g}Jarab abur.u wu\v{c} luhu-zwa-t'a? \\
    \Pt[] they(\Erg[]) what:\Abs[] say-\Impf[]-\Cond[] \\
    ``I wonder what they are saying.'' (427)
    \bg.\label{sent:ex4h}Ada-z im axwar ja-ni, xabar ja-ni \v{c}i-zwa-\v{c}-ir. \\
    he-\Dat[] [this:\Abs[] dream \Cop[]-\Q[] news \Cop[]-\Q[]] know-\Impf[]-\Neg[]-\Pst[] \\
    ``He did not know whether this was dream or reality.'' (426)
    \z.


\ex. Relative clause, Adjective based on preposition: c.f. Figure \ref{fig:ex2} \\
    \ag.\label{sent:ex2a}[Kolxoz.di-n ja\v{s}aji\v{s}.di-kaj k\^{x}e-nwa-j] rasskaz-ar \\
        [kolkhoz-\Gen[] life-\Sbelc[] write-\Prf[]-\Ptcp[]] story-\Pl[] \\
        ``stories about collective farm life" (252)
    \bg.\label{sent:ex2b}revoljucija.di-laj wilikan \"{u}m\"{u}r \\
        revolution-\Obl[]-\Srelc[] previous life \\
        ``life before the revolution" (252)
    \z.
    
    
\ex. Demonstratives co-occuring with each other or determiners \\
    \ag.\label{sent:ex6a}Ha i klass.d-a sa mus jat'ani za-ni k'el-na-j. \\
    that this class-\Inessc[] one when \Indf[] I:\Erg[]-also study-\Aori[]-\Pst[] \\
    ``At one time I, too, was a student in this classroom." (191)
    \bg.\label{sent:ex6b}i zi kic' \\
    this I:\Gen[] dog \\
    ``this my dog" (not: \textit{*dog of this I}) (261)
    \z.

\ex. \label{sent:ex3}Postpositions \ref{fig:sent3}\\
    \ag.\label{sent:ex3a}Kac stol.di-n k'anik aka\^{x}-na. \\
        cat table-\Gen[] under enter-\Aori[] \\
        ``The cat went under the table." (170) 
    \bg.\label{sent:ex3b}Kac stol.di-n k'anikaj xkec'-na. \\
        cat table-\Gen[] from.under go.out-\Aori[] \\
        ``The cat came out from under the table." (170)
    \z.

\ex.\label{sent:ex5} Ergative and dative subject preceding absolutive argument \\
    \ag. Alfija.di ma\~{q}ala k\^{x}e-na \\
        Alfija(\Erg[]) article write-\Aori[] \\
        ``Alifja wrote an article'' (294)
    \bg. Mu?minat.a-z Ibrahim aku-na \\
        Mu'minat-\Dat[] Ibrahim see-\Aori \\
        ``Mu'minat saw Ibrahim'' (294)
    \z.

\ex.\label{sent:ex8}Coreferential Omission \\
    \ag.\label{sent:ex8a}Ada jar\v{g}-ar.i-z kilig-un dawamar-na. \\
    he(\Erg[]) [distance-\Pl[]-\Dat[] look-\Masd[]] continue-\Aori[] \\
    ``He kept looking into the distance.'' (295)
    \bg.\label{sent:ex8b}G\"{u}ldeste wiri \v{z}\"{u}re.di-n k'walax-ar awu-n.i-z ma\v{z}bur \^{x}a-na. \\
    G\"{u}ldeste [all kind-\Gen[] work-\Pl[] do-\Masd[]-\Dat[]] forced become-\Aori[] \\
    ``G\"{u}ldeste was forced to do work of all kinds.'' (295)
    \cg.\label{sent:ex8c}Wa-z k\"{u}\v{c}e.di-z fi-n.i-kaj ki\v{c}e-zwa-ni? \\
    you-\Dat[] [street-\Dat[] go-\Masd[]-\Sbelc[]] afraid-\Impf[]-\Q[] \\
    ``Are you afraid to go on the street?''
    \z.

\exg.\label{sent:ex9}Za \v{c}er\v{c}enie.d-in tars hazur-zawa. \\
    I:\Erg[] drawing-\Gen[] lesson prepare-\Impf[] \\
    ``I'm preparing the drawing lesson.'(140)

\ex.Aorist\\
    \ag.\label{sent:ex11a}Sadwil.i wa aq'ulluwil.i abur \~{q}utarmi\v{s}-na \\
    unity(\Erg[]) and cleverness(\Erg[]) they save-\Aori[] \\
    ``Unity and cleverness saved them.'' (142)
    \bg.\label{sent:ex11b}Alat-aj jis.u-z Dilber.a q'we predmet.d-aj pis \~{q}imet-ar \~{q}a\v{c}u-na-j. \\
    [pass-\Aop[]] year-\Dat[] Dilber(\Erg[]) two subject-\Inel[] bad grade-\Pl[] take-\Aori[]-\Pst[] \\
    ``The year before, Dilber had gotten bad grades in two subjects.'' (143)
    \z.

\ex.Perfect\\
    \ag.\label{sent:ex12a}Zun q\"{u}z\"{u} \^{x}a-nwa, \v{c}an ru\v{s}. \\
    I:\Abs[] old become-\Prf[] soul girl \\
    ``I have become old, my girl'' (143)
    \bg.\label{sent:ex12b}Zi pul na a\~{q}ud-nawa! \\
    I:\Gen[] money you:\Erg[] take.away-\Prf[] \\
    ``YOU have stolen my money!'' [the theft has just occurred] (143)
    \z.

\ex.Future \\
    \ag.\label{sent:ex10a}Zun x\"{u}r.\"{u}-z $q^h$fi-da. \\
    I:\Abs[] village-\Dat[] go.back-\Fut[] \\
    ``I'll go back to the village'' (141)
    \bg.\label{sent:ex10b}Pa\v{c}ah awa-\v{c}-iz \v{c}un hik' dulanmi\v{s} \v{z}e-da? \\
    king be.in-\Neg[]-\Imc[] we:\Abs[] how living be-\Fut[] \\
    ``How shall we live without the king?'' (141)
    \z.

